---
title: "case study"
output: html_document
---

```{r setup, include=FALSE}
library(tidyverse)
library(viridis)
library(leaflet)

knitr::opts_chunk$set(
  echo = TRUE,
  warning = FALSE,
  fig.width = 8,
  fig.height = 6,
  out.wideth = "90%"
)

options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)

scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d

theme_set(theme_minimal() + theme(legend.position = "bottom"))
```


## do some data science

```{r}
library(p8105.datasets)
data("nyc_airbnb")
```

* how are airbnb prices related to rent in the neighborhood?
* which neighborhood is the most expensive, which is the most cheapest?
* do hosts with multiple sites have higher prices or rating?
* does price has relation to ratings?
* is average length of stay related to neighbood? price? etc?

## answer the questions

```{r}
nyc_airbnb = 
  nyc_airbnb %>% 
  mutate(
    stars = review_scores_location / 2,
    borough = neighbourhood_group
  )
```

```{r}
nyc_airbnb %>% 
  mutate(
    neighbourhood = as.factor(neighbourhood)) %>% 
  filter(borough == "Manhattan") %>% 
  mutate(
    neighbourhood = fct_reorder(neighbourhood, price)) %>% 
  ggplot(aes(x = price, y = neighbourhood)) +
  geom_violin()
```


## answer another question

```{r}
price_neighborhood = 
  select(nyc_airbnb, neighbourhood, price) %>% 
  group_by(neighbourhood) %>% 
  summarise(
    mean_price = mean(price)
  ) %>% 
  arrange(-mean_price)
price_neighborhood
```


```{r}
nyc_airbnb %>% 
  group_by(borough, room_type) %>% 
  summarize(med_price = median(price, na.rm = TRUE)) %>% 
  pivot_wider(
    names_from = room_type,
    values_from = med_price
  )
```

```{r}
nyc_airbnb %>% 
  filter(borough == "Staten Isaland", room_type == "Shared romm")
```

```{r}
nyc_airbnb %>% 
  count(borough, room_type) %>% 
  pivot_wider(
    names_from = room_type,
    values_from = n
  )
```

```{r}
nyc_airbnb %>% 
  group_by(neighbourhood_group, neighbourhood) %>% 
  summarize(
    mean_price = mean(price, na.rm = TRUE),
    mean_review = mean(review_scores_location, na.rm = TRUE)
  ) %>% 
  ggplot(aes(x = mean_review, y = mean_price)) + 
  geom_point() +
  facet_grid(~neighbourhood_group)
```

```{r}
nyc_airbnb %>% 
  count(neighbourhood)
```

```{r}
nyc_airbnb %>% 
  filter(neighbourhood == "Astoria") %>% 
  ggplot(aes(x = stars, y = price)) +
  geom_point()
```


## something that is very fancy!

```{r}
pal <- colorNumeric(
  palette = "viridis",
  domain = nyc_airbnb$stars
)

nyc_airbnb %>% 
  filter(
    borough == "Manhattan",
    price > 2000) %>% 
  leaflet() %>% 
  addTiles() %>% 
  addProviderTiles(providers$CartoDB.Positron) %>% 
  addCircleMarkers(
    ~lat, ~long,
    color = ~pal(stars),
    radius = 1)
```

another siilar chunk of code

```{r}
pal <- colorNumeric(
  palette = "viridis",
  domain = nyc_airbnb$stars
)

nyc_airbnb %>% 
  filter(borough == "Manhattan") %>% 
  mutate(
    label = str_c("<b>Stars: ", stars, "</b><br>Price: ", price , sep = "")
  ) %>% 
  sample_n(1000) %>% 
  leaflet() %>% 
  addTiles() %>% 
  addProviderTiles(providers$CartoDB.Positron) %>% 
  addCircleMarkers(
    ~lat, ~long,
    color = ~pal(stars),
    radius = 1, 
    popup = ~ label)
```













